Effect Sizes

### 2018-05-30 effect sizes/effect_sizes.Rmd
Updated effect size stuff for CIs

Another way to think about this analysis is that it tests whether the underlying effect parameters are the same.
To see this, note that $T_1$ being contained in the 95\% confidence interval for $\theta_2$ is equivalent to 
\[
S = |T_1 - T_2|/\sqrt{v_2} \leq 1.96
\]
This is conceptually identical to testing a null hypothesis of $H_0: \theta_1 = \theta_2$ with test statistic $S$ being compared to a standard normal distribution.
However, under $H_0$, $S$ does not follow a standard normal distribution.

>>>>

Another way to think about this analysis is that it tests whether the underlying effect parameters are the same.
To see this, note that $T_1$ being contained in the 95\% confidence interval for $\theta_2$ is equivalent to 
\[
S = |T_1 - T_2|/\sqrt{v_2} \leq 1.96
\]
This is conceptually identical to testing a null hypothesis of $H_0: \theta_1 = \theta_2$ with test statistic $S$ being compared to a standard normal distribution.
However, under $H_0$, $S$ does not follow a standard normal distribution.
Instead, it follows a normal distribution with mean zero and variance $1 + v_1/v_2$.

If $\theta_1 = \theta_2$, then we would like this test to conclude that the studies replicate.
This would require $S$ to be smaller than 1.96 in magnitude. 
The probability that $S$ exceeds 1.96 would be the Type I error rate. 
The exact error rate is given by:
\[
1 - \Phi\left(\frac{1.96}{\sqrt{1 + v_1/v_2}}\right) + \Phi\left(\frac{-1.96}{\sqrt{1 + v_1/v_2}}\right)
\]
If study 1 is much larger than study 2, so that $v_1/v_2$ is close to zero, than this error rate will be close to nominal---that is, the Type I error rate will be close to 0.05.
However, the error rate will be increasing as $v_1/v_2$ gets larger. 
If both studies are the same size so that $v_1 = v_2$, then the error rate is 32.7\%. 
If study 2 is twice the size of study 1, so that $v_1 = v_2/2$, then the error rate is 51.4\%.

[INSERT FIGURE? error rate vs. v1/v2]

If, however, $\theta_1 \neq \theta_2$ we would want the test to determine that the studies do not replicate, so that $S$ is at least as large as 1.96 in magnitude.
